---
title: "Psychosis Project - Regression and ANOVA tables"
author: T. Bryan Jackson
organization: TAMU, Psychological and Brain Sciences 
output:

  pdf_document: 
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 4
---

# Load Libraries

```{r message = FALSE, warning = FALSE}
library("ggplot2")
library("brms")
library("caret")
library("jtools")
library("multcomp")
library("emmeans")
library("apaTables")
library("papaja")
```


# Prepare Dataset

Set Up Group Factor, Split Dataset, etc.

## Load Dataset

```{r inlcude = FALSE}
setwd("~/Desktop/PsychosisProject/Analyses")
raw_data <- read.csv("~/Desktop/PsychosisProject/Analyses/Data.csv")
dataset = raw_data
dataset$Group <- as.factor(dataset$Group)
dataset$Group <- factor(dataset$Group, levels=c('HC', 'CHR', 'ECP', 'CP'))

set.seed(4)

dataset_4 = split(dataset,dataset$Group)
CP = dataset_4$CP
ECP = dataset_4$ECP
CHR = dataset_4$CHR
HC = dataset_4$HC

noHC = rbind(CHR, ECP, CP)
```

## Descriptive Stats

```{r}
summary(dataset)

```

### HC

```{r}
summary(HC)
sd(HC$Age, na.rm=TRUE)
sd(HC$Alcohol, na.rm=TRUE)
sd(HC$Marj, na.rm=TRUE)
sd(HC$CPZ_eqiuv, na.rm=TRUE)
sd(HC$PANSS.P, na.rm=TRUE)
sd(HC$PANSS.N, na.rm=TRUE)
sd(HC$PANSS.Cog, na.rm=TRUE)
sd(HC$SIPS.P, na.rm=TRUE)
sd(HC$SIPS.N, na.rm=TRUE)

```

### CHR

```{r}
summary(CHR)
sd(CHR$Age, na.rm=TRUE)
sd(CHR$Alcohol, na.rm=TRUE)
sd(CHR$Marj, na.rm=TRUE)
sd(CHR$CPZ_eqiuv, na.rm=TRUE)
sd(CHR$PANSS.P, na.rm=TRUE)
sd(CHR$PANSS.N, na.rm=TRUE)
sd(CHR$PANSS.Cog, na.rm=TRUE)
sd(CHR$SIPS.P, na.rm=TRUE)
sd(CHR$SIPS.N, na.rm=TRUE)
```

### ECP

```{r}
summary(ECP)
sd(ECP$Age, na.rm=TRUE)
sd(ECP$Alcohol, na.rm=TRUE)
sd(ECP$Marj, na.rm=TRUE)
sd(ECP$CPZ_eqiuv, na.rm=TRUE)
sd(ECP$PANSS.P, na.rm=TRUE)
sd(ECP$PANSS.N, na.rm=TRUE)
sd(ECP$PANSS.Cog, na.rm=TRUE)
sd(ECP$SIPS.P, na.rm=TRUE)
sd(ECP$SIPS.N, na.rm=TRUE)
```

### CP

```{r}
summary(CP)
sd(CP$Age, na.rm=TRUE)
sd(CP$Alcohol, na.rm=TRUE)
sd(CP$Marj, na.rm=TRUE)
sd(CP$CPZ_eqiuv, na.rm=TRUE)
sd(CP$PANSS.P, na.rm=TRUE)
sd(CP$PANSS.N, na.rm=TRUE)
sd(CP$PANSS.Cog, na.rm=TRUE)
sd(CP$SIPS.P, na.rm=TRUE)
sd(CP$SIPS.N, na.rm=TRUE)
```

# Group Differences in Symptoms

## PANSS-P
```{r}
GroupDiffPP <- aov(PANSS.P ~ Group + Alcohol+ Marj + Age + CPZ_eqiuv, dataset)
summary(GroupDiffPP)
PANSS_P_group_plot <- effect_plot(GroupDiffPP, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
PANSS_P_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank(), axis.title.y = element_blank())

posthoc_PP <- glht(GroupDiffPP, linfct = mcp(Group="Tukey"))
summary(posthoc_PP, adjusted(type='fdr'))

```

## PANSS-N
```{r}

GroupDiffPN <- aov(PANSS.N ~ Group + Alcohol+ Marj + Age + CPZ_eqiuv, dataset)
summary(GroupDiffPN)
PANSS_N_group_plot <- effect_plot(GroupDiffPN, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
PANSS_N_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank(), axis.title.y = element_blank())

posthoc_PN <- glht(GroupDiffPN, linfct = mcp(Group="Tukey"))
summary(posthoc_PN, adjusted(type='fdr'))

```

## PANSS-Cog
```{r}

GroupDiffPC <- aov(PANSS.Cog ~ Group + Alcohol+ Marj + Age  + CPZ_eqiuv, dataset)
summary(GroupDiffPC)
PANSS_Cog_group_plot <- effect_plot(GroupDiffPC, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
PANSS_Cog_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank(), axis.title.y = element_blank())

```

## SIPS-P
```{r}

GroupDiffSP <- aov(SIPS.P ~ Group + Alcohol + Marj + Age , dataset)
summary(GroupDiffSP)
SIPS_P_group_plot <- effect_plot(GroupDiffSP, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
SIPS_P_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank(), axis.title.y = element_blank())

posthoc_SP <- glht(GroupDiffSP, linfct = mcp(Group="Tukey"))
summary(posthoc_SP, adjusted(type='fdr'))

```

## SIPS-N
```{r}

GroupDiffSN <- aov(SIPS.N ~ Group + Alcohol+ Marj + Age, dataset)
summary(GroupDiffSN)
SIPS_N_group_plot <- effect_plot(GroupDiffSN, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
SIPS_N_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank(), axis.title.y = element_blank())

posthoc_SN <- glht(GroupDiffSN, linfct = mcp(Group="Tukey"))
summary(posthoc_SN, adjusted(type='fdr'))

```




# Group Differences in CB-BG GE

## CCBN
```{r}
GroupDiffC <- aov(CCBN ~ Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, dataset)
summary(GroupDiffC)
CCBN_group_plot <- effect_plot(GroupDiffC, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
CCBN_group_plot + ylab("CCBN GE") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank())

posthoc_C <- glht(GroupDiffC, linfct = mcp(Group="Tukey"))
summary(posthoc_C, adjusted(type='fdr'))

```

## MCBN
```{r}

GroupDiffM <- aov(MCBN ~ Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, dataset)
summary(GroupDiffM)
MCBN_group_plot <- effect_plot(GroupDiffM, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
MCBN_group_plot + ylab("MCBN GE") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank())

posthoc_M <- glht(GroupDiffM, linfct = mcp(Group="Tukey"))
summary(posthoc_M, adjusted(type='fdr'))

```


# Group Differences in Cort GE

## FPN

```{r}
GroupDiffFPN <- aov(FPN ~ Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, dataset)
summary(GroupDiffFPN)
FPN_group_plot <- effect_plot(GroupDiffFPN, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
FPN_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank())

posthoc_FPN <- glht(GroupDiffFPN, linfct = mcp(Group="Tukey"))
summary(posthoc_FPN, adjusted(type='fdr'))

```

## CON
```{r}

GroupDiffCON <- aov(CON ~ Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, dataset)
summary(GroupDiffCON)
CON_group_plot <- effect_plot(GroupDiffCON, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
CON_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank())

posthoc_CON <- glht(GroupDiffCON, linfct = mcp(Group="Tukey"))
summary(posthoc_CON, adjusted(type='fdr'))

```

## DMN
```{r}

GroupDiffDMN <- aov(DMN ~ Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, dataset)
summary(GroupDiffDMN)
DMN_group_plot <- effect_plot(GroupDiffDMN, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
DMN_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank())

posthoc_DMN <- glht(GroupDiffDMN, linfct = mcp(Group="Tukey"))
summary(posthoc_DMN, adjusted(type='fdr'))

```

## EN
```{r}

GroupDiffEN <- aov(EN ~ Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, dataset)
summary(GroupDiffEN)
EN_group_plot <- effect_plot(GroupDiffEN, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
EN_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank())

posthoc_EN <- glht(GroupDiffEN, linfct = mcp(Group="Tukey"))
summary(posthoc_EN, adjusted(type='fdr'))

```

## MN
```{r}

GroupDiffMN <- aov(MN ~ Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, dataset)
summary(GroupDiffMN)
MN_group_plot <- effect_plot(GroupDiffMN, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
MN_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank())

posthoc_MN <- glht(GroupDiffMN, linfct = mcp(Group="Tukey"))
summary(posthoc_MN, adjusted(type='fdr'))

```

## AN
```{r}

GroupDiffAN <- aov(AN ~ Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, dataset)
summary(GroupDiffAN)
AN_group_plot <- effect_plot(GroupDiffAN, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
AN_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank())

posthoc_AN <- glht(GroupDiffAN, linfct = mcp(Group="Tukey"))
summary(posthoc_AN, adjusted(type='fdr'))

```

## VN
```{r}

GroupDiffVN <- aov(VN ~ Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, dataset)
summary(GroupDiffVN)
VN_group_plot <- effect_plot(GroupDiffVN, pred = Group, interval = TRUE, partial.residuals = TRUE, jitter = .2)
VN_group_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1), axis.title.x = element_blank())

posthoc_VN <- glht(GroupDiffVN, linfct = mcp(Group="Tukey"))
summary(posthoc_VN, adjusted(type='fdr'))

```
# CB-BG GE predicts Cort GE

## FPN
```{r}
FPN_4groups <- lm(FPN ~ CCBN*MCBN*Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, data = dataset)
summary(FPN_4groups)
FPN_CCBN_plot <- effect_plot(FPN_4groups, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
FPN_CCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1))
FPN_MCBN_plot <- effect_plot(FPN_4groups, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
FPN_MCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
trellis.par.set(par.axis.text=list(cex=1.25))
trellis.par.set(par.strip.text=list(cex=2))
trellis.par.set(par.xlab.text=list(fontsize=0))
trellis.par.set(par.ylab.text=list(fontsize=0))

xyplot(FPN ~ CCBN | Group, data=dataset, fit = FPN_4groups, par.settings = list(strip.background=list(col="lightgrey"), par.strip.text = list(fontsize=20)),
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })
xyplot(FPN ~ MCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })

```

## CON
```{r}

CON_4groups <- lm(CON ~ CCBN*MCBN*Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, data = dataset)
summary(CON_4groups)
CON_CCBN_plot <- effect_plot(CON_4groups, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
CON_CCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
CON_MCBN_plot <- effect_plot(CON_4groups, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
CON_MCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
xyplot(FPN ~ CCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })
xyplot(FPN ~ MCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })
```

## DMN
```{r}

DMN_4groups <- lm(DMN ~ CCBN*MCBN*Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, data = dataset)
summary(DMN_4groups)
DMN_CCBN_plot <- effect_plot(DMN_4groups, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
DMN_CCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
DMN_MCBN_plot <- effect_plot(DMN_4groups, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
DMN_MCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
xyplot(DMN ~ CCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })
xyplot(DMN ~ MCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })

```

## EN
```{r}

EN_4groups <- lm(EN ~ CCBN*MCBN*Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, data = dataset)
summary(EN_4groups)
EN_CCBN_plot <- effect_plot(EN_4groups, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
EN_CCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
EN_MCBN_plot <- effect_plot(EN_4groups, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
EN_MCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
xyplot(EN ~ CCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })
xyplot(EN ~ MCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })
```

## MN
```{r}

MN_4groups <- lm(MN ~ CCBN*MCBN*Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, data = dataset)
summary(MN_4groups)
MN_CCBN_plot <- effect_plot(MN_4groups, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
MN_CCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
MN_MCBN_plot <- effect_plot(MN_4groups, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
MN_MCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
xyplot(MN ~ CCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })
xyplot(MN ~ MCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })

```

## VN
```{r}

VN_4groups <- lm(VN ~ CCBN*MCBN*Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, data = dataset)
summary(VN_4groups)
VN_CCBN_plot <- effect_plot(VN_4groups, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
VN_CCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
VN_MCBN_plot <- effect_plot(VN_4groups, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
VN_MCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
xyplot(VN ~ CCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })
xyplot(VN ~ MCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })

```

## AN
```{r}

AN_4groups <- lm(AN ~ CCBN*MCBN*Group + Alcohol+ Marj + Age + Dataset + CPZ_eqiuv, data = dataset)
summary(AN_4groups)
AN_CCBN_plot <- effect_plot(AN_4groups, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
AN_CCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
AN_MCBN_plot <- effect_plot(AN_4groups, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
AN_MCBN_plot + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
xyplot(AN ~ CCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })
xyplot(AN ~ MCBN | Group, data=dataset, par.settings = list(strip.background=list(col="lightgrey")), 
  panel = function(x, y, ...) {
       panel.xyplot(x, y, ..., col = "black")
       panel.lmline(x, y, col = "black")
  })
```

## Combined table 
```{r}
export_summs(FPN_4groups, CON_4groups,DMN_4groups,EN_4groups,MN_4groups, VN_4groups,AN_4groups, to.file = "docx", file.name = "models.docx", model.names = c("FPN", "CON", "DMN", "EN", "MN", "VN", "AN"))
```


# Predicting Symptoms - Across All Groups (incl. HC)

## PANSS-P
```{r}
PANSS_P_all <- lm(PANSS.P ~ CCBN + MCBN + Alcohol + Marj + Age + Dataset + CPZ_eqiuv, data = dataset)
summary(PANSS_P_all)
PANSS_P_CCBN_all_plot <- effect_plot(PANSS_P_all, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
PANSS_P_CCBN_all_plot + ylab("PANSS-P") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1))
PANSS_P_MCBN_all_plot <- effect_plot(PANSS_P_all, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
PANSS_P_MCBN_all_plot + ylab("PANSS-P") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 

```

## PANSS-N
```{r}

PANSS_N_all <- lm(PANSS.N ~ CCBN + MCBN + Alcohol + Marj + Age + Dataset + CPZ_eqiuv, data = dataset)
summary(PANSS_N_all)
PANSS_N_CCBN_all_plot <- effect_plot(PANSS_N_all, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
PANSS_N_CCBN_all_plot + ylab("PANSS-N") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
PANSS_N_MCBN_all_plot <- effect_plot(PANSS_N_all, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
PANSS_N_MCBN_all_plot + ylab("PANSS-N") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 

```

## PANSS-Cog
```{r}

PANSS_C_all <- lm(PANSS.Cog ~ CCBN + MCBN + Alcohol + Marj + Age + CPZ_eqiuv, data = dataset)
summary(PANSS_C_all)
PANSS_Cog_CCBN_all_plot <- effect_plot(PANSS_C_all, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
PANSS_Cog_CCBN_all_plot + ylab("PANSS-Cog") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
PANSS_Cog_MCBN_all_plot <- effect_plot(PANSS_C_all, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
PANSS_Cog_MCBN_all_plot + ylab("PANSS-Cog") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 

```

## SIPS-P
```{r}
SIPS_P_all <- lm(SIPS.P ~ CCBN + MCBN + Alcohol + Marj + Age, data = dataset)
summary(SIPS_P_all)
SIPS_P_CCBN_all_plot <- effect_plot(SIPS_P_all, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
SIPS_P_CCBN_all_plot + ylab("SIPS-P") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
SIPS_P_MCBN_all_plot <- effect_plot(SIPS_P_all, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
SIPS_P_MCBN_all_plot + ylab("SIPS-P") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 

```

## SIPS-N
```{r}

SIPS_N_all <- lm(SIPS.N ~ CCBN + MCBN + Alcohol + Marj + Age, data = dataset)
summary(SIPS_N_all)
SIPS_N_CCBN_all_plot <- effect_plot(SIPS_N_all, pred = CCBN, interval = TRUE, partial.residuals = TRUE)
SIPS_N_CCBN_all_plot + ylab("SIPS-N") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 
SIPS_N_MCBN_all_plot <- effect_plot(SIPS_N_all, pred = MCBN, interval = TRUE, partial.residuals = TRUE)
SIPS_N_MCBN_all_plot + ylab("SIPS-N") + theme(text = element_text(size = 24), panel.border = element_rect(colour = "black", fill=NA, size=1)) 

```

## Combined table 
```{r}
export_summs(PANSS_P_all, PANSS_N_all, PANSS_C_all, SIPS_P_all, SIPS_N_all, to.file = "docx", file.name = "models_symptoms.docx", model.names = c("PANSS-P", "PANSS-N", "PANSS-C", "SIPS-P", "SIPS-N"))
```
